---
title: "Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
## The Webgraph package is still under development, some features may not be working right now. 

In this article, we will introduce you to the basics of Webgraph. 


You can first install the Webgraph package through the `install_github()` function of the `devtools` package : 

```{r setup}
library(devtools)
install_github("Paulogcd/Webgraph", quiet = TRUE)
```

## How to make edgelists 

The main feature of the Webgraph package is creating edgelists of webpages connections. For that, several options are possible, depending on the number of webpages you are collecting data on : 

1. Several webpages 
2. Several webpages around one target
3. One webpage

### Several webpages

In the case that you want to collect the data of connections between several webpages around one target, it is recommended that you use the `edgelists_of()` function. 

This function still needs to be implemented. 

### Several webpages around one target

In the case that you want to collect the data of the network formed by the connections of pages aoround one main target, it is recommended that you use the `network_from_webpage()` function. Currently, only the prototype `network_from_webpage1()` function exists. This function takes not only the target as a parameter, but also the `iteration` value, that is the number of levels you want the scrapping process to go. You can use it as : 

```{r}
library(Webgraph)
library(igraph)
target = "http://google.com"
n <- network_from_webpage1(target, iteration = 2)
g <- graph_from_data_frame(n)
plot(g,
     layout=layout_with_fr,
     vertex.size=4,
     vertex.label=NA,
     vertex.label.dist=0.5,
     vertex.color="red",
     edge.arrow.size=0.5)
```

### One webpage

In the case that you want to collect the data of the links of only one page, you can use the `edgelist_of()` or the `network_from_webpage1()` (with `iteration=1`) functions. You can use them as : 

```{r}
target = "http://google.com"

# Function graph_from_webpage() :

g1 <- graph_from_webpage(target)
plot(g1,
     layout=layout_with_fr,
     vertex.size=4,
     vertex.label=NA,
     vertex.label.dist=0.5,
     vertex.color="red",
     edge.arrow.size=0.5)

# Function network_from_webpage1 :
n2 <- network_from_webpage1(target, iteration = 1)
g2 <- graph_from_data_frame(n2)
plot(g2,
     layout=layout_with_fr,
     vertex.size=4,
     vertex.label=NA,
     vertex.label.dist=0.5,
     vertex.color="red",
     edge.arrow.size=0.5)
```